\textbf{{\Large {Recurrent relation for branching coefficients of affine Lie algebras}}}

### 2009-11-07 AffineLieAlgebras/InformalNotes/article.tex
New items in the bibliography, some work on the physical applications and placement of the figures.

We show the result of this procedure on the figure \ref{fig:B4B2anom}.
\begin{figure}[ph]
    \includegraphics[width=170mm]{B4_B2_anom_points.pdf}
  \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$
\begin{figure}[ph]
  \includegraphics[width=150mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

\begin{figure}[ph]
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the figure
\begin{figure}[ph]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$. 
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \includegraphics[width=150mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:B4B2Fan}
\end{figure}

@@

Using the recurrent relation for the anomalous branching coefficients we get the following result
\begin{figure}[ph]
  \includegraphics[width=150mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.
\section{Physical applications}
\label{sec:phys-appl}
\begin{comment}
  Rewrite it in more scientific style or drop this section.
\end{comment}
Branching coefficients for the embedding of affine Lie subalgebra into
affine Lie algebra can be used to construct modular invariant
partition functions of Wess-Zumino-Novikov-Witten models.

>>>>

We show the result of this procedure on the figure \ref{fig:B4B2anom}.
\begin{figure}[h]
    \includegraphics[width=170mm]{B4_B2_anom_points.pdf}
  \caption{Anomalous points with the dimensions of corresponding $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:B4B2anom}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$
\begin{figure}[h]
  \includegraphics[width=150mm]{B4_B2_fan.pdf}
  \caption{Fan for $B_2\subset B_4$}
  \label{fig:B4B2Fan}
\end{figure}
We use the recurrent relation (\ref{recurrent relation}) and get
following branching coefficients:
\begin{equation}
  \label{eq:24}
  \pi_{\mathfrak{a}} \left(ch L^{(0,1,0,2)}_{B_4}\right) = 6 \; ch L^{(0,0)}_{B_2}+ 60
  \; ch L_{B_2}^{(0,2)}+ 30 \; ch L_{B_2}^{(1,0)}+ 19 \; ch L_{B_2}^{(2,0)}+
  40 \; ch L_{B_2}^{(1,2)}+ 10 \; ch L_{B_2}^{(2,2)}
\end{equation}
The dimension of the highest-weight $B_4$-module $L^{(0,1,0,2)}_{B_4}$
is equal to 2772. It is easy to see, that right-hand side of the
equation (\ref{eq:24}) gives the same result.

@@

\begin{figure}[h!tb]
  \includegraphics[width=160mm]{AffineB2_A1_Anom.pdf}
  \caption{The anomalous points of the $(1,0,1,0)$ representation of the algebra $\hat{B_2}$}
  \label{fig:affine_B2_anom_point}
\end{figure}

As the next step of our algorithm \ref{sec:algorithm} we project the anomalous points to the weight space of the subalgebra $\hat{A_1}$ and calculate the dimensions of the corresponding $\mathfrak{a}_{\bot}$-modules $L^{\pi_{\mathfrak{a}_{\bot}}(\omega(\mu+\rho))-\rho_{\mathfrak{a}_{\bot}}}_{\mathfrak{a}_{\bot}}$.
The result of this computation up to the twelfth grade is presented at the figure
\begin{figure}[h!tb]
  \centering
  \includegraphics[width=150mm]{AffineB2_A1_proj_anom.pdf}
  \caption{Projected anomalous points and the dimensions of $\mathfrak{a}_{\bot}$-modules.}
  \label{fig:AffineB2_A1_anom_proj}
\end{figure}

@@

Using the definition (\ref{fan-defined}) we get the following set of
the points $\Gamma$ with the corresponding values $s(\gamma+\gamma_0)$. 
Here we restricted the computation to the twelfth grade.
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_fan.pdf}
  \caption{Fan for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:B4B2Fan}
\end{figure}

@@

Using the recurrent relation for the anomalous branching coefficients we get the following result
\begin{figure}[ph]
  \centering
  \includegraphics[width=130mm]{AffineB2_A1_branching.pdf}
  \caption{Anomalous branching coefficients for $\hat{A_1}\subset \hat{B_2}$}
  \label{fig:AffineB2_A1_branching}
\end{figure}

Selecting the points inside the main Weyl chamber of the subalgebra $\hat{A_1}$ we get the following results for the branching coefficients up to twelfth grade
\begin{multline}
  \label{eq:28}
  L^{w_1}_{\hat{B_2}\downarrow \hat{A_1}}=2 L_{\hat{A_1}}^{w_1}(0)\oplus 1 L_{\hat{A_1}}^{w_0}(0)\oplus 4 L_{\hat{A_1}}^{w_0}(-1)\oplus\\
    2 L_{\hat{A_1}}^{w_1}(-1)\oplus 8 L_{\hat{A_1}}^{w_0}(-2)\oplus
    8 L_{\hat{A_1}}^{w_1}(-2)\oplus 15 L_{\hat{A_1}}^{w_0}(-3)\oplus\\
    12 L_{\hat{A_1}}^{w_1}(-3)\oplus 26 L_{\hat{A_1}}^{w_1}(-4)\oplus
    29 L_{\hat{A_1}}^{w_0}(-4)\oplus 51 L_{\hat{A_1}}^{w_0}(-5)\oplus\\
    42 L_{\hat{A_1}}^{w_1}(-5)\oplus 78 L_{\hat{A_1}}^{w_1}(-6)\oplus
    85 L_{\hat{A_1}}^{w_0}(-6)\oplus 120 L_{\hat{A_1}}^{w_1}(-7)\oplus\\
    139 L_{\hat{A_1}}^{w_0}(-7)\oplus 202 L_{\hat{A_1}}^{w_1}(-8)\oplus
    222 L_{\hat{A_1}}^{w_0}(-8)\oplus 306 L_{\hat{A_1}}^{w_1}(-9)\oplus\\
    346 L_{\hat{A_1}}^{w_0}(-9)\oplus 530 L_{\hat{A_1}}^{w_0}(-10)\oplus
    482 L_{\hat{A_1}}^{w_1}(-10)\oplus 714 L_{\hat{A_1}}^{w_1}(-11)\oplus\\
    797 L_{\hat{A_1}}^{w_0}(-11)\oplus 1080 L_{\hat{A_1}}^{w_1}(-12)\oplus
    1180 L_{\hat{A_1}}^{w_0}(-12)
\end{multline}
This result can be expressed using the power series expansion of the branching functions \cite{kac1990idl}.
\begin{eqnarray}
  \label{eq:29}
  \begin{array}{cc}
    b^{(w_1)}_{0}= & 1 + 4\,q^{1}+ 8\,q^{2}+ 15\,q^{3}+ 29\,q^{4}+ 51\,q^{5}+ 85\,q^{6}+ 139\,q^{7}+\\
     &222\,q^{8}+ 346\,q^{9}+ 530\,q^{10}+ 797\,q^{11}+ 1180\,q^{12}+\dots\\
  \end{array}\\
  \begin{array}{cc}
    b^{(w_1)}_{1}= &2+2\,q^{1}+8\,q^{2}+12\,q^{3}+26\,q^{4}+42\,q^{5}+78\,q^{6}+120\,q^{7}+\\
    & 202\,q^{8}+306\,q^{9}+482\,q^{10}+714\,q^{11}+1080\,q^{12}+\dots
  \end{array}
\end{eqnarray}
Here the lower index of the branching function denotes the number of the corresponding $\hat{A_1}$ fundamental weight $w_0=\lambda_0=(0,1,0),\; w_1=\alpha/2=(1,1,0)$.

\newpage
\section{Physical applications}
\label{sec:phys-appl}
Here we want to discuss possible applications of the described techniques in physical models.

Branching coefficients for the embedding of affine Lie subalgebra into
affine Lie algebra can be used to construct modular invariant
partition functions of Wess-Zumino-Novikov-Witten models (\cite{difrancesco1997cft}, \cite{Walton:1999xc}, \cite{walton1989conformal}, \cite{schellekens1986conformal}).

But for this construction to work the embedding is required to be conformal, which means that the central charge of the subalgebra is equal to the central charge of the algebra.
\begin{equation}
  \label{eq:31}
  c(\mathfrak{a})=c(\mathfrak{g})
\end{equation}

 The class of the conformal embeddings is rather small, the complete classification is given in the paper \cite{schellekens1986conformal}. 
The requirement (\ref{eq:31}) allows to reduce the task of the computation of the branching coefficients of affine Lie algebras to the computation of the branching coefficients of the finite-dimensional Lie algebras.

Here we describe this procedure and discuss how the requirement (\ref{eq:31}) can be used to simplify the algorithm \ref{sec:algorithm}.
